IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-09-15 main.tex
:pencil: Update manuscript

			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) IRS not only provides constructive reflection but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

@@

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}. First, it is observed that adding either active or passive elements can improve the equivalent SNR and produce a nearly concave R-E region, which suggests that the receiver should operate in the PS mode in such cases. Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design. To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}. As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs. Third, passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious in the case of WIT and WPT. For active beamforming, doubling $M$ brings a \SI{3}{\dBA} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC ends up with a nearly four-time (\SI{12}{\dBA}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dBA}, which implies a reflect array gain of $L^2$ \cite{Wu2019}. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC by \num{16} times (\SI{24}{\dBA}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.

@@

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system. Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region. A three-stage BCD algorithm was proposed to solve the problem. In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition. In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method. We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity. Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design. Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order. However, a large number of reflecting elements may be required to compensate the double fading effect in the auxiliary link.

@@

			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.

>>>>

			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design; 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

@@

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}. First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver. Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design. To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}. As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs. Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the diode nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}. Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC. From the perspective of WIT, passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model. This novel observation is then verified in a simplified case where we assume the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct link is negligible. The DC in such case reduces to
		\begin{equation}
			z = \beta_2 \lvert h_{\mathrm{R}} h_{\mathrm{I}} \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \lvert h_{\mathrm{R}} h_{\mathrm{I}} \rvert^4 L^4 P^2,
		\end{equation}
		which scales quartically with $L$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.

@@

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system. Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region. A three-stage BCD algorithm was proposed to solve the problem. In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition. In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method. We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity. Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design. Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design. Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of waveform design.

@@

			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in \cite[Appendix~A]{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
